Patient-Specific Neural Field Modeling from Micro-Electrode Data

### 2010-07-26 ltx/data_paper/DataPaper.tex
edits to kernel support section the homogeniety test bit

Figure~\ref{fig:SpatialCrossCorrelation} shows the average (across time) cross-correlations between consecutive field observations for the different time periods relative to the seizure progression. By averaging over time, the effect of the disturbance is reduced. The subplots of the figure show that the connectivity kernel exhibits local excitation with surround inhibition. The plot indicate the support for excitatory aspect of the kernel centred at the origin is -2 mm to 2 mm in the x direction and slightly wider in the y direction.

The assumption of homgeneity can be tested by performing the correlation analysis 
\begin{itemize}
	\item it is difficult to tell what correlations are from the cross-talk due the the sensor kernel
	\item it is difficult because of the nonlinear function
	\item 
\end{itemize}

>>>>

Figure~\ref{fig:SpatialCrossCorrelation} shows the average (across time) cross-correlations between consecutive field observations for the different time periods of the seizure progression. By averaging over time, the effect of the disturbance is reduced allowing for the support of the kernel to be seen. The subplots of the figure show that the connectivity kernel exhibits local excitation with surround inhibition. The plots indicate the support for excitatory aspect of the kernel centred at the origin is -2~mm to 2~mm in the $x$ direction and slightly wider in the $y$ direction.

The assumption of homogeneity was tested by performing the cross-correlation analysis on 4 equal sized subsections of the field observations. The subsections consisted $6\times6$ electrode grids, such that they overlapped by one electrode row and column. The overlap was required so the subsections where large enough for the support of the kernel to be seen in the cross-correlation analysis. The results of the analysis can be seen in Figure~\ref{fig:HomogeneityTest}. The results indicate that...
